Trauma treatment delay

### 2023-11-16 manuscriptlongversion.Rmd
text

@@

>>>>

As the table below shows, most of the variables, when adjusted for, does
not have an effect on the risk of receiving delayed treatment. Only two
values in one of the categories had an effect, having ICU or OR compared
to having ER as your highest care level. It suggests that patients who
were in the ICU or OR as their highest care level had a lower chance of
receiving delayed treatment compared with patients who had ER as their
highest.

@@

The analysis shows that when adjusted for, most variables do not have a
correlation with receiving delayed treatment.
